Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation

### 2017-10-04 inst/doc/draft/draft2.Rmd
hypervolume update

---
title: Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India
author: "Sylvain Schmitt sylvain.schmitt@agroparistech.fr"
date: '`r Sys.Date()`'
csl: mee.csl
bibliography: refs.bib
knit: "bookdown::render_book"
output:
  bookdown::gitbook
---

@@

```{r hypervolume, fig.cap='Functional hypervolume overlap of canopy and understorey species.'}
bd <- Q %>% 
  filter(!is.na(WES)) %>% 
  select(-LES, -WES, -SpCode, -strata) %>% 
  summarise_all(funs(sd)) %>% 
  unlist()
CalcOverlap <- function(traits_strata){
  hv <- lapply(traits_strata, function(strata) 
    hypervolume::hypervolume(strata[names(bd)], bandwidth = bd, verbose = F))
  set <- hypervolume::hypervolume_set(hv$C, hv$U, check_memory = F, verbose = F)
  hypervolume::hypervolume_sorensen_overlap(set)
}
overlap <- Q %>% 
  filter(!is.na(WES)) %>% 
  select(-LES, -WES, -SpCode) %>% 
  split(., .$strata) %>% 
  CalcOverlap()
# cl <- makeCluster(cores)
# clusterExport(cl, list('Q', 'CalcOverlap', 'bd'))
# n_overlap <- parSapply(cl, 1:n, function(i) {
#   library(dplyr)
#   Q %>% 
#     filter(!is.na(WES)) %>% 
#     select(-LES, -WES, -SpCode) %>% 
#     mutate(strata = sample(strata)) %>% 
#     split(., .$strata) %>% 
#     CalcOverlap()
# })
# stopCluster(cl)
# save(n_overlap, file = file.path(path, 'overlap.Rdata'))
load(file.path(path, 'overlap.Rdata'))
data.frame(x = n_overlap) %>% 
  ggplot(aes(x)) +
  geom_density() +
  geom_vline(xintercept = overlap,
             col = 'red') +
  ggtitle(paste('pvalue =', 
                round((rank(c(overlap, n_overlap))/(n+1))[1], 3))) +
  xlab('Overlap null distribution')
```

@@

```{r hypervolume2}
data <- Q %>% 
  filter(!is.na(WES)) %>% 
  select(-LES, -WES, -SpCode) %>% 
  split(., .$strata)
hv <- lapply(data, function(strata) 
    hypervolume::hypervolume(strata[names(bd)], bandwidth = bd, verbose = F))
set <- hypervolume::hypervolume_set(hv$C, hv$U, check_memory = F, verbose = F)
hv <- list(C = set@HVList$Unique_1,
           U = set@HVList$Unique_2,
           Intersect = set@HVList$Intersection)
plot(hypervolume::hypervolume_join(hv$C, hv$U))
hv <- list(C = data$C[
  hypervolume::hypervolume_inclusion_test(hv$C, data$C[names(bd)]),],
           U = data$U[
  hypervolume::hypervolume_inclusion_test(hv$U, data$U[names(bd)]),],
           Intersect = do.call('rbind', data)[
  hypervolume::hypervolume_inclusion_test(hv$Intersect, 
                                          do.call('rbind', data)[names(bd)]),])

>>>>

---
title: Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India
author: "Sylvain Schmitt sylvain.schmitt@agroparistech.fr"
date: '`r Sys.Date()`'
csl: mee.csl
bibliography: refs.bib
knit: "bookdown::render_book"
output:
  bookdown::gitbook
  # bookdown::pdf_book
  # word_document
---

@@

```{r hypervolume, eval=FALSE, fig.cap='Functional hypervolume overlap of canopy and understorey species.'}
bd <- Q %>% 
  filter(!is.na(WES)) %>% 
  select(-LES, -WES, -SpCode, -strata) %>% 
  summarise_all(funs(sd)) %>% 
  unlist()
CalcOverlap <- function(traits_strata){
  hv <- lapply(traits_strata, function(strata) 
    hypervolume::hypervolume(strata[names(bd)], kde.bandwidth = bd, verbose = F))
  set <- hypervolume::hypervolume_set(hv$C, hv$U, check.memory = F, verbose = F)
  hypervolume::hypervolume_overlap_statistics(set)
}
overlap <- Q %>% 
  filter(!is.na(WES)) %>% 
  select(-LES, -WES, -SpCode) %>% 
  split(., .$strata) %>% 
  CalcOverlap()
# cl <- makeCluster(cores)
# clusterExport(cl, list('Q', 'CalcOverlap', 'bd'))
# n_overlap <- parSapply(cl, 1:n, function(i) {
#   library(dplyr)
#   Q %>%
#     filter(!is.na(WES)) %>%
#     select(-LES, -WES, -SpCode) %>%
#     mutate(strata = sample(strata)) %>%
#     split(., .$strata) %>%
#     CalcOverlap()
# })
# stopCluster(cl)
# save(n_overlap, file = file.path(path, 'overlap.Rdata'))
load(file.path(path, 'overlap.Rdata'))
data.frame(x = n_overlap) %>% 
  ggplot(aes(x)) +
  geom_density() +
  geom_vline(xintercept = overlap,
             col = 'red') +
  ggtitle(paste('pvalue =', 
                round((rank(c(overlap, n_overlap))/(n+1))[1], 3))) +
  xlab('Overlap null distribution')
summary(overlap$C)
CalcOverlap(overlap$C, overlap$U)
```

@@

```{r hypervolume2, eval=FALSE}
data <- Q %>% 
  filter(!is.na(WES)) %>% 
  select(-LES, -WES, -SpCode) %>% 
  split(., .$strata)
hv <- lapply(data, function(strata) 
    hypervolume::hypervolume(strata[names(bd)], bandwidth = bd, verbose = F))
set <- hypervolume::hypervolume_set(hv$C, hv$U, check_memory = F, verbose = F)
hv <- list(C = set@HVList$Unique_1,
           U = set@HVList$Unique_2,
           Intersect = set@HVList$Intersection)
plot(hypervolume::hypervolume_join(hv$C, hv$U))
hv <- list(C = data$C[
  hypervolume::hypervolume_inclusion_test(hv$C, data$C[names(bd)]),],
           U = data$U[
  hypervolume::hypervolume_inclusion_test(hv$U, data$U[names(bd)]),],
           Intersect = do.call('rbind', data)[
  hypervolume::hypervolume_inclusion_test(hv$Intersect, 
                                          do.call('rbind', data)[names(bd)]),])

### 2017-10-04 inst/doc/draft_mrm.Rmd
hypervolume update

>>>>

```{r hypervolume}
data <- PFT_sp[-which(is.na(PFT_sp$WD)), c('LA', 'WD', 'LT', 'LDMC', 'SLA', 'strata')]
bd <- estimate_bandwidth(data[-6])
C <- hypervolume(subset(data, strata == 'C')[-6], bandwidth = bd, name = 'C')
U <- hypervolume(subset(data, strata == 'U')[-6], bandwidth = bd, name = 'U')
UC <- new("HypervolumeList", HVList = list(C = C, U = U))
set <- hypervolume_set(C, U, check_memory = F)
hypervolume_sorensen_overlap(set)
get_volume(set)
```
